Does at-issueness predict projection? Further investigations of the Gradient Projection Principle

### 2022-11-06 writing/investigating-GPP.tex
made small changes to paper
added data summary and graphs for projection data

@@

\ex Is the at-issueness of contents positively correlated under different measures of at-issueness?
\end{xlist}
\end{exe}

@@

We recruited 250-300 participants for each of Exps.~1-3. Participants for Exp.~1q were recruited on Amazon's Mechanical Turk platform; the participants were required to have U.S.\ IP addresses and at least 99\% of previously approved HITs. Participants for the remaining experiments were recruited on Prolific; these participants were required to reside in the US, to be born in the US, to have English as their first language, and to have an approval rating of at least 99\%. Information on the participants and the exclusion criteria is provided in Supplement \ref{a-participants}.

>>>>

Prijection comparison hasn't been done, except in CommitmentBank paper (right?, perhaps A'dam colloquium presentation?).

@@

\ex Is the at-issueness of contents positively correlated under different measures of at-issueness?

\ex Compare projection under different entailment-cancelling operators

\ex Do commonly used at-issueness diagnostics work for content embedded under entailment-cancelling operators?

@@

We recruited 250-300 participants for each of the 12 experiments. Participants for Exp.~1q were recruited on Amazon's Mechanical Turk platform; the participants were required to have U.S.\ IP addresses and at least 99\% of previously approved HITs. Participants for the remaining experiments were recruited on Prolific; these participants were required to reside in the US, to be born in the US, to have English as their first language, and to have an approval rating of at least 99\%. Information on the participants and the exclusion criteria is provided in Supplement \ref{a-participants}.
